### 2016-02-23 ch02-qlogms/excitation-design.tex
Remove some unneeded files

\subsection{Generic system}
%TODO: explain generic LTI system
Consider a second-order subsystem
\begin{equation}
  G_2(s, \theta) = \frac{K \wn^{2 \multiplicity} \left( s + \wz \right)}{\wz \left(s^2 + 2 \damping \wn s + \wn^2 \right)^{\multiplicity}}
\end{equation}
parametrized in $\theta =  \left[K, \wn, \wz, \damping \right]^{\T}$.
To determine the Fisher Information matrix, the derivative $\PartialDerivative{G(s,\theta)}{\theta}$ is required; its components are given by:
\begin{align}
  \PartialDerivative{G_2}{K} 
    &= 
  \frac{\wn^{2\multiplicity}}{\wz}
  \frac{s + \wz}{\left(s^2 + 2 \damping \wn s + \wn^2\right)^{\multiplicity}}
  \\
  \PartialDerivative{G_2}{\wz} 
    &= 
    \frac{-K \wn^{2\multiplicity}}
              {\wz} 
    \frac{s}
              {\left(s^2 + 2 \damping \wn s + \wn^2\right)^{\multiplicity}} 
  \\
  \PartialDerivative{G_2}{\wn} 
  &= 
  \frac{2 K \wn^{2\multiplicity-1} \multiplicity}
            {\wz} 
  \frac{\left( s + \wz \right) \left( s+ \damping \wn \right)}
            {\left( s^2 + 2 \damping \wn s + \wn^2 \right)^{\multiplicity + 1}}
  \\
  \PartialDerivative{G_2}{\damping}
  &= 
  \frac{-2 K \wn^{2\multiplicity + 1} \multiplicity}
            {\wz}
  \frac{s \left( s + \wz \right)}
             {\left( s^2 + 2 \damping \wn s + \wn^2 \right)^{\multiplicity + 1}}
  \text{.}
\end{align}

@@

  \begin{remark}
  All simulations  have been repeated fitted with the \MATLAB System Identification Toolbox by means of the \mcode{oe} function~\citep{TDIDENT}.
  The observed results were identical and hence are not elaborated further in this text.
  \end{remark}

@@

% \input{ch02-qlogms/sysid.tex}

>>>>

\subsection{Generic system}
%TODO: explain generic LTI system
Consider the second-order subsystem with multiplicity $\multiplicity$:
\begin{equation}
  G_2(s, \theta) = \frac{K \wn^{2 \multiplicity} \left( s + \wz \right)}{\wz \left(s^2 + 2 \damping \wn s + \wn^2 \right)^{\multiplicity}}
\end{equation}
parametrized in $\theta =  \left[K, \wn, \wz, \damping \right]^{\T}$.
To determine the Fisher Information matrix, the derivative $\PartialDerivative{G(s,\theta)}{\theta}$ is required; its components are given by:
\begin{align}
  \PartialDerivative{G_2}{K} 
    &= 
  \frac{\wn^{2\multiplicity}}{\wz}
  \frac{s + \wz}{\left(s^2 + 2 \damping \wn s + \wn^2\right)^{\multiplicity}}
  \\
  \PartialDerivative{G_2}{\wz} 
    &= 
    \frac{-K \wn^{2\multiplicity}}
              {\wz} 
    \frac{s}
              {\left(s^2 + 2 \damping \wn s + \wn^2\right)^{\multiplicity}} 
  \\
  \PartialDerivative{G_2}{\wn} 
  &= 
  \frac{2 K \wn^{2\multiplicity-1} \multiplicity}
            {\wz} 
  \frac{\left( s + \wz \right) \left( s+ \damping \wn \right)}
            {\left( s^2 + 2 \damping \wn s + \wn^2 \right)^{\multiplicity + 1}}
  \\
  \PartialDerivative{G_2}{\damping}
  &= 
  \frac{-2 K \wn^{2\multiplicity + 1} \multiplicity}
            {\wz}
  \frac{s \left( s + \wz \right)}
             {\left( s^2 + 2 \damping \wn s + \wn^2 \right)^{\multiplicity + 1}}
  \text{.}
\end{align}

@@

  \begin{remark}
  All simulations  have been repeated as well by fitting with the \MATLAB System Identification Toolbox by means of the \mcode{oe} function~\citep{TDIDENT}.
  The observed results were similar and hence are not elaborated further in this text.
  For more information, please refer to \citep{Larsson2012SYSID}.
  \end{remark}

@@
